Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-15 manuscript/climate_sensitivity_draft.Rmd
Added mean Rc and Rs #144

At the community level, cored trees showed substantial growth reductions in all three droughts, with a mean $Rt$ of 0.86 in 1966 and 1999, and 0.84 in 1977  (Fig. **1b**). Across the entire study period (1950-2009), the focal drought years were the three years with the largest fraction of trees exhibiting $Rt \le 0.7$. Specifically, in each drought, roughly 30% of the cored trees had growth reductions of $\ge$ 30% ($Rt \le 0.7$): 29% in 1966, 32% in 1977, and 27% in 1999. However, some individuals exhibited increased growth, *i.e.*, $Rt > 1.0$: 26% of trees in 1966, 22% in 1977, and 26% in 1999. 
Recovery was generally strong, with $Rc$ averaging **##** in 1966, **##**in 1977, and **##** in 1999 (Fig. **S6**), and $Rs$ averaging **##** in 1966, **##**in 1977, and **##** in 1999 (Fig. **1c**).

>>>>

At the community level, cored trees showed substantial growth reductions in all three droughts, with a mean $Rt$ of 0.86 in 1966 and 1999, and 0.84 in 1977  (Fig. **1b**). Across the entire study period (1950-2009), the focal drought years were the three years with the largest fraction of trees exhibiting $Rt \le 0.7$. Specifically, in each drought, roughly 30% of the cored trees had growth reductions of $\ge$ 30% ($Rt \le 0.7$): 29% in 1966, 32% in 1977, and 27% in 1999. However, some individuals exhibited increased growth, *i.e.*, $Rt > 1.0$: 26% of trees in 1966, 22% in 1977, and 26% in 1999. 
Recovery was generally strong, with $Rc$ averaging **1.55** in 1966, **1.42**in 1977, and **1.34** in 1999 (Fig. **S6**), and $Rs$ averaging **1.28** in 1966, **1.19**in 1977, and **1.12** in 1999 (Fig. **1c**).
